SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-11 scipy-1.0/paper.tex
Add paragraph re: funding (w/ Stefan)

>>>>

\subsection*{Funding}

%100,000 annual salary, 112 person-years, 414,473 lines of code -> 11,192,622 (https://www.openhub.net/p/scipy/estimated\_cost, which uses the Basic COCOMO model).

The development cost of SciPy is estimated in excess of 10M dollars by
OpenHub.  Yet, the project is largely unfunded, having been
developed predominantly by graduate students, faculty, and members of industry
in their free time. Small amounts of funding have been applied with success:
some meetings were sponsored by universities and industry, Google's Summer of Code
program supported infrastructure and algorithmic work, and teaching grant funds were
used early on to develop documentation.  However, these small amounts of
sporadic funding are not commensurate with the enormous stack of important scientific
software, like those that are used to plan national space missions, that rely
on SciPy.  In the traditional academic funding model, it is easy to support
commercial software, but hard to provide funds for community driven projects,
and as more science depends on open source software national funding agencies
urgently need to pay attention to this challenge. And, unlike for commercial
software where a license seat encompasses all development (and other) costs, agencies will
have to tolerate the more diverse spending required to do planning and maintain
infrastructure if these open source projects are to remain a healthy
underpinning infrastructure for international scientific endeavors.

%largely unfunded
%- graduate students
%- faculty
%- industry program
%
%-- free time
%
%Small funds:
%- meetings (eg Berkeley)
%- GSOC (test infrastructure, recently FFT work, been doing it since, what 2011/2012/2013?)
%- documentation
%
%Problems:
%- funding agencies (NIH, NSF, etc.)
%- foundation have few mechanism for support, while ironically able to fund e.g. Matlab licenses
%- difficulty of hiring full time dev for community projects
%
%Rec:
%- Funders need to address
%- Funding needs to be carefully used to support the community; not just technical work but also process, roadmap, discussing and deciding for new features, etc.
%
%- Many stakeholders, supporting space missions, entire fields, ...
